ms_willow_network_supplement

### 2015-04-06 ms_willow_network_supplement.Rmd
created figure for simulation and ordination complementarity

>>>>

Qualitative differences in gall community composition?
```{r vegan galls}
gall.comm <- full.df %>% select(Genotype, vLG_abund, rG_abund, aSG_abund, SG_abund)
gall.comm.sub <- filter(gall.comm, rowSums(gall.comm[ ,-1]) > 0, 
                        Genotype != "J", Genotype != "N", Genotype != "U")
table(gall.comm.sub$Genotype)

gall.comm.raupcrick <- raupcrick(gall.comm.sub[ ,-1])

adonis(gall.comm.raupcrick ~ Genotype, gall.comm.sub)
